Quantifying passive kelp rafting phenomena and connectivity of nearshore communities around the coast of South Africa through development of a 3D spectral numerical coastal-flow model

### 2020-07-08 thesis_chapter_1.Rmd
chapter 1 output updated and general tidyup of associated rmd file

---
title: Quantifying passive kelp rafting phenomena and connectivity of nearshore communities around the coast of South Africa through development of a 3D spectral numerical coastal-flow model
author:
- R Coppin^[University of the Western Cape]
- C Rautenbach^[South African Weather Service]
- AJ Smit^[University of the Western Cape]
output:
  html_document:
    df_print: paged
    theme: simplex
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    fig_caption: yes
    reference_docx: markdown/thesis_template.docx
    toc: yes
bibliography: references.bib
---

@@

```{r surface elevation figures, echo=FALSE, warning=FALSE, fig.align="center", fig.cap="\\label{fig:surface elevation figures}The definition of a wave in a time record of the surface elevation with downward zero-crossings (upper panel) and upward zero-crossings (lower panel)."}

@@

```{r Hs_Tp_surface_elevation figure, echo=FALSE, warning=FALSE, fig.align="center", fig.cap="The definition of wave height and wave period in a time record of the surface elevation (the wave is defined with downwrd zero-crossings."}

@@

```{r BF_1, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 3, fig.height = 3, fig.align="center", fig.cap='\\label{fig:BF_1}Conceptual model of bouyancy characteristics.'}

>>>>

---
title: Quantifying passive kelp rafting phenomena and connectivity of nearshore communities around the coast of South Africa through development of a 3D spectral numerical coastal-flow model
author:
- R Coppin^[University of the Western Cape]
- C Rautenbach^[South African Weather Service]
- AJ Smit^[University of the Western Cape]
output:
  word_document:
    fig_caption: yes
    reference_docx: markdown/thesis_template.docx
    toc: yes
  pdf_document:
    toc: yes
  html_document:
    df_print: paged
    theme: simplex
    toc: yes
bibliography: references.bib
---

@@

```{r surface elevation figures, echo=FALSE, warning=FALSE, fig.cap="\\label{fig:surface elevation figures}The definition of a wave in a time record of the surface elevation with downward zero-crossings (upper panel) and upward zero-crossings (lower panel)."}

@@

```{r Hs_Tp_surface_elevation figure, echo=FALSE, warning=FALSE, fig.cap="The definition of wave height and wave period in a time record of the surface elevation (the wave is defined with downwrd zero-crossings."}

@@

```{r BF_1, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 3, fig.height = 3, fig.cap='\\label{fig:BF_1}Conceptual model of bouyancy characteristics.'}
